|

### 2020-03-30 inst/manuscript/candidaev_supplement.Rmd
Fix minor typos in supplement

```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=fS1_args, dpi=600}
# construct figure 1
fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           seperate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

@@

# export table S2 LaTeX code with \\ line endings removed in a text file
tabS1_clean <- gsub("\\\\\\\\\n", "\n", tabS1)

cat(tabS1_clean, file = "tables/table_S1.txt", sep = "\n")

@@

# export table S2 LaTeX code with \\ line endings removed in a text file
tabS2_clean <- gsub("\\\\\\\\\n", "\n", tabS2)

cat(tabS2_clean, file = "tables/table_S2.txt", sep = "\n")

@@

```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
fS4_cap <- c("\\textbf{Differential abundance analysis of proteins identified 
              in EVs isolated from two different morphologies of the DAY286 
              \\textit{C. albicans} strain.} \\textit{(A)} Venn diagram 
              comparing the biofilm EV and yeast EV proteome data sets shown 
              in Figure 2A. \\textit{(B)} Volcano plot depicting significantly 
              enriched biofilm EV or yeast EV proteins. Differential abundance 
              analysis was performed by comparing the mean normalised LFQ
              intensities of common DAY286 EV proteins (i.e. proteins in the 
              Venn overlap) using the package \\textit{limma} (ref:limma). 
              Significantly enriched proteins were identified using a 
              Benjamini-Hochberg adjusted p-value cut-off of 0.01 and a 
              log\\textsubscript{2}(FC) cut-off of 1. Counts of significant and 
              non-significant proeins are indicated. Proteins with a
              log\\textsubscript{2}(FC) greater than 5 or less than -5 are 
              labelled. Data underlying this plot are provided in 
              Supplementary Data S6.")

@@

```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
fS5_cap <- c("\\textbf{Functional enrichment analyses of EVs from two DAY286 
              morphologies.} Top 10 signficantly enriched biological process 
              (BP), cellular component (CC), and molecular function (MF) GO 
              terms for the \\textit{(A)} yeast EV enriched and exclusive proteins or
              \\textit{(B)} biofilm EV enriched or exclusive proteins shown in 
              Supplementary Figure S4. GO analyses were performed using 
              the online tool FungiFun2 (elbe.hki-jena.de/fungifun) 
              (Hypergeometric distribution, Benjamini-Hochberg adjusted 
              p-value < 0.01)
              (ref:fungifun). The GO terms are presented top to bottom in order 
              of increasing adjusted p-value. Full lists of enriched GO terms
              can be found in Supplementary Data S7.")

>>>>

```{r figureS1, fig.cap=fS1_cap, fig.width=5.45, fig.height=6, fig.path='figures/', dev=c('pdf', 'tiff'), dev.args=fS1_args, dpi=600}
# construct figure 1
fS1_cap <- "\\textbf{Schematic of the workflow used for the isolation and 
           proteomic analysis of \\textit{C. albicans} EVs and the selection 
           of EV protein markers.} Steps 1 to 6 were performed for each of the 
           four strains examined in this study: DAY286 yeast, ATCC90028 yeast, 
           ATCC10231 yeast, and DAY286 biofilm. The results from the four 
           separate analyses were combined (step 7) to identify proteins which 
           commonly appeared as EV marker candidates. The MISEV2018 criteria 
           for protein content-based EV characterisation and other 
           considerations were used to select the best \\textit{C. albicans} 
           EV marker proteins."

@@

@@

# export table S2 LaTeX code (to be converted to docx with Pandoc)
cat(tabS2, file = "tables/table_S2.tex", sep = "\n")

@@

```{r figureS4, fig.cap=fS4_cap, fig.height=6, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS4_args, dpi=600}
fS4_cap <- c("\\textbf{Differential abundance analysis of proteins identified 
              in EVs isolated from two different morphologies of the DAY286 
              \\textit{C. albicans} strain.} \\textit{(A)} Venn diagram 
              comparing the biofilm EV and yeast EV proteome data sets shown 
              in Figure 2A. \\textit{(B)} Volcano plot depicting significantly 
              enriched biofilm EV or yeast EV proteins. Differential abundance 
              analysis was performed by comparing the mean normalised LFQ
              intensities of common DAY286 EV proteins (i.e. proteins in the 
              Venn overlap) using the package \\textit{limma} (ref:limma). 
              Significantly enriched proteins were identified using a 
              Benjamini-Hochberg adjusted p-value cut-off of 0.01 and a 
              log\\textsubscript{2}(FC) cut-off of 1. Counts of significant and 
              non-significant proteins are indicated. Proteins with a
              log\\textsubscript{2}(FC) greater than 5 or less than -5 are 
              labelled. Data underlying this plot are provided in 
              Supplementary Data S6.")

@@

```{r figureS5, fig.cap=fS5_cap, fig.height=7, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS5_args, dpi=600}
fS5_cap <- c("\\textbf{Functional enrichment analyses of EVs from two DAY286 
              morphologies.} Top 10 significantly enriched biological process 
              (BP), cellular component (CC), and molecular function (MF) GO 
              terms for the \\textit{(A)} yeast EV enriched and exclusive proteins or
              \\textit{(B)} biofilm EV enriched or exclusive proteins shown in 
              Supplementary Figure S4. GO analyses were performed using 
              the online tool FungiFun2 (elbe.hki-jena.de/fungifun) 
              (Hypergeometric distribution, Benjamini-Hochberg adjusted 
              p-value < 0.01)
              (ref:fungifun). The GO terms are presented top to bottom in order 
              of increasing adjusted p-value. Full lists of enriched GO terms
              can be found in Supplementary Data S7.")

### 2020-03-30 inst/manuscript/tables/table_S2.tex
Fix minor typos in supplement

\caption{\label{tab:}\textbf{Candidate negative protein markers for 

@@

\hspace{1em}ARO3 & Phospho-2-dehydro-3-deoxyheptonate aldolase<sup>b</sup> & -1.28 & -2.55 & -1.51 & -1.46 &  &  & \\
\hspace{1em}ARO8 & Aromatic transaminase of the Ehrlich fusel oil pathway<sup>a</sup> & -2.37 & -1.81 & ex & -2.36 &  &  & \\

@@

\hspace{1em}HOM2 & Aspartate-semialdehyde dehydrogenase<sup>b</sup> & ex & -3.41 & ex & ex &  &  & \\
\hspace{1em}orf19.1889 & Putative phosphoglycerate mutase family protein<sup>b</sup> & ex & -1.60 & ex & ex &  &  & \\
\hspace{1em}orf19.5943.1 & \textit{S. cerevisiae} ortholog is Stm1, regulates translation<sup>a</sup> & ex & -3.98 & -4.57 & ex &  &  & \\
\hspace{1em}orf19.6596 & Putative esterase<sup>a</sup> & ex & ex & ex & -2.90 &  &  & \\
\hspace{1em}orf19.7263 & Putative X-Pro aminopeptidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}SBP1 & \textit{S. cerevisiae} ortholog is Sbp1, eIF4G binding protein<sup>a</sup> & ex & -4.30 & -3.80 & -2.15 &  &  & \\
\hspace{1em}STI1 & HSP90 co-chaperone<sup>a</sup> & ex & -2.20 & ex & ex &  &  & \\
\hspace{1em}URA4 & Predicted succinate semialdehyde dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}XKS1 & Putative xylulokinase<sup>b</sup> & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}ACH1 & Acetyl-CoA hydrolase<sup>b</sup> & -3.24 & -5.09 & -2.79 & -4.03 &  &  & \\
\hspace{1em}GLR1 & Glutathione reductase<sup>b</sup> & ex & ex & ex & -3.28 &  &  & \\
\hspace{1em}HSP60 & Heat shock protein 60<sup>b</sup> & -4.66 & -1.59 & -4.22 & -4.06 &  &  & \\

@@

\hspace{1em}AAT1 & Aspartate aminotransferase<sup>a</sup> & ex & -2.11 & -1.48 & -5.70 &  &  & \\
\hspace{1em}BAT22 & Putative branched chain amino acid aminotransferase<sup>b</sup> & ex & -3.57 & -1.44 & -3.12 &  &  & \\
\hspace{1em}ETR1 & Putative 2-enoyl thioester reductase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}GCV2 & Glycine decarboxylase P subunit<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}IDH1 & Isocitrate dehydrogenase subunit<sup>a</sup> & -2.67 & -2.48 & -1.85 & -2.22 &  &  & \\
\hspace{1em}IDH2 & Isocitrate dehydrogenase<sup>a</sup> & -3.21 & -2.88 & -3.54 & -3.37 &  &  & \\
\hspace{1em}IDP1 & Putative isocitrate dehydrogenase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}ILV5 & Ketol-acid reductoisomerase<sup>b</sup> & -3.68 & -2.62 & -2.27 & -5.48 &  &  & \\
\hspace{1em}KGD2 & Putative dihydrolipoamide S-succinyltransferase<sup>a</sup> & ex & -2.20 & -2.04 & ex &  &  & \\

@@

\hspace{1em}NIF3 & \textit{S. cerevisiae} ortholog is Nif3, mitochondrial protein<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.2966 & Predicted dienelactone hydrolase domain<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.449 & Putative phosphatidyl synthase<sup>b</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.7215.3 & \textit{S. cerevisiae} ortholog is Hsp10, mitochondrial co-chaperonin<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}PDX3 & Pyridoxamine-phosphate oxidase<sup>a</sup> & ex & -1.85 & ex & ex &  &  & \\

@@

\hspace{1em}DOT5 & Thioredoxin peroxidase<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}NHP6A & Non-histone chromosomal protein 6<sup>a</sup> & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}AMS1 & Putative alpha-mannosidase<sup>a</sup> & ex & ex & ex & -2.23 &  &  & \\

@@

\hspace{1em}orf19.2755 & \textit{S. cerevisiae} ortholog is Pre7, Beta 6 subunit of 20S proteasome<sup>a</sup> & ex & -2.34 & ex & ex &  &  & \\
\hspace{1em}orf19.4230 & 20S proteasome subunit (beta7)<sup>a</sup> & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}SCL1 & Proteasome subunit YC7alpha<sup>a</sup> & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}TIF11 & Translation initiation factor eIF1a<sup>a</sup> & ex & ex & ex & ex &  &  & \\
\hspace{1em}TMA19 & \textit{S. cerevisiae} ortholog is Tma19, ribosome associated protein<sup>a</sup> & ex & -3.05 & -2.74 & ex &  &  & \\

@@

\hspace{1em}orf19.1433 & \textit{S. cerevisiae} ortholog is Lpx1, peroxisomal lipase<sup>a</sup> & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}orf19.2125 & Protein of unknown function<sup>c</sup> & ex & ex & ex & ex & 1 &  & \\
\hspace{1em}orf19.2737 & Carbohydrate kinase domain-containing protein<sup>c</sup> & ex & ex & ex & -1.48 &  &  & \\
\hspace{1em}orf19.5620 & Stationary phase enriched protein<sup>c</sup> & ex & ex & ex & -3.43 &  &  & \\
\hspace{1em}OYE32 & NADPH oxidoreductase family protein<sup>c</sup> & ex & ex & ex & -2.90 &  &  & \\

>>>>

\caption{(\#tab:tableS2)\textbf{Candidate negative protein markers for 

@@

\hspace{1em}ARO3 & Phospho-2-dehydro-3-deoxyheptonate aldolase\textsuperscript{b} & -1.28 & -2.55 & -1.51 & -1.46 &  &  & \\
\hspace{1em}ARO8 & Aromatic transaminase of the Ehrlich fusel oil pathway\textsuperscript{a} & -2.37 & -1.81 & ex & -2.36 &  &  & \\

@@

\hspace{1em}HOM2 & Aspartate-semialdehyde dehydrogenase\textsuperscript{b} & ex & -3.41 & ex & ex &  &  & \\
\hspace{1em}orf19.1889 & Putative phosphoglycerate mutase family protein\textsuperscript{b} & ex & -1.60 & ex & ex &  &  & \\
\hspace{1em}orf19.5943.1 & \textit{S. cerevisiae} ortholog is Stm1, regulates translation\textsuperscript{a} & ex & -3.98 & -4.57 & ex &  &  & \\
\hspace{1em}orf19.6596 & Putative esterase\textsuperscript{a} & ex & ex & ex & -2.90 &  &  & \\
\hspace{1em}orf19.7263 & Putative X-Pro aminopeptidase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}SBP1 & \textit{S. cerevisiae} ortholog is Sbp1, eIF4G binding protein\textsuperscript{a} & ex & -4.30 & -3.80 & -2.15 &  &  & \\
\hspace{1em}STI1 & HSP90 co-chaperone\textsuperscript{a} & ex & -2.20 & ex & ex &  &  & \\
\hspace{1em}URA4 & Predicted succinate semialdehyde dehydrogenase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}XKS1 & Putative xylulokinase\textsuperscript{b} & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}ACH1 & Acetyl-CoA hydrolase\textsuperscript{b} & -3.24 & -5.09 & -2.79 & -4.03 &  &  & \\
\hspace{1em}GLR1 & Glutathione reductase\textsuperscript{b} & ex & ex & ex & -3.28 &  &  & \\
\hspace{1em}HSP60 & Heat shock protein 60\textsuperscript{b} & -4.66 & -1.59 & -4.22 & -4.06 &  &  & \\

@@

\hspace{1em}AAT1 & Aspartate aminotransferase\textsuperscript{a} & ex & -2.11 & -1.48 & -5.70 &  &  & \\
\hspace{1em}BAT22 & Putative branched chain amino acid aminotransferase\textsuperscript{b} & ex & -3.57 & -1.44 & -3.12 &  &  & \\
\hspace{1em}ETR1 & Putative 2-enoyl thioester reductase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}GCV2 & Glycine decarboxylase P subunit\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}IDH1 & Isocitrate dehydrogenase subunit\textsuperscript{a} & -2.67 & -2.48 & -1.85 & -2.22 &  &  & \\
\hspace{1em}IDH2 & Isocitrate dehydrogenase\textsuperscript{a} & -3.21 & -2.88 & -3.54 & -3.37 &  &  & \\
\hspace{1em}IDP1 & Putative isocitrate dehydrogenase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}ILV5 & Ketol-acid reductoisomerase\textsuperscript{b} & -3.68 & -2.62 & -2.27 & -5.48 &  &  & \\
\hspace{1em}KGD2 & Putative dihydrolipoamide S-succinyltransferase\textsuperscript{a} & ex & -2.20 & -2.04 & ex &  &  & \\

@@

\hspace{1em}NIF3 & \textit{S. cerevisiae} ortholog is Nif3, mitochondrial protein\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.2966 & Predicted dienelactone hydrolase domain\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.449 & Putative phosphatidyl synthase\textsuperscript{b} & ex & ex & ex & ex &  &  & \\
\hspace{1em}orf19.7215.3 & \textit{S. cerevisiae} ortholog is Hsp10, mitochondrial co-chaperonin\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}PDX3 & Pyridoxamine-phosphate oxidase\textsuperscript{a} & ex & -1.85 & ex & ex &  &  & \\

@@

\hspace{1em}DOT5 & Thioredoxin peroxidase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}NHP6A & Non-histone chromosomal protein 6\textsuperscript{a} & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}AMS1 & Putative alpha-mannosidase\textsuperscript{a} & ex & ex & ex & -2.23 &  &  & \\

@@

\hspace{1em}orf19.2755 & \textit{S. cerevisiae} ortholog is Pre7, Beta 6 subunit of 20S proteasome\textsuperscript{a} & ex & -2.34 & ex & ex &  &  & \\
\hspace{1em}orf19.4230 & 20S proteasome subunit (beta7)\textsuperscript{a} & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}SCL1 & Proteasome subunit YC7alpha\textsuperscript{a} & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}TIF11 & Translation initiation factor eIF1a\textsuperscript{a} & ex & ex & ex & ex &  &  & \\
\hspace{1em}TMA19 & \textit{S. cerevisiae} ortholog is Tma19, ribosome associated protein\textsuperscript{a} & ex & -3.05 & -2.74 & ex &  &  & \\

@@

\hspace{1em}orf19.1433 & \textit{S. cerevisiae} ortholog is Lpx1, peroxisomal lipase\textsuperscript{a} & ex & ex & ex & ex &  &  & \\

@@

\hspace{1em}orf19.2125 & Protein of unknown function\textsuperscript{c} & ex & ex & ex & ex & 1 &  & \\
\hspace{1em}orf19.2737 & Carbohydrate kinase domain-containing protein\textsuperscript{c} & ex & ex & ex & -1.48 &  &  & \\
\hspace{1em}orf19.5620 & Stationary phase enriched protein\textsuperscript{c} & ex & ex & ex & -3.43 &  &  & \\
\hspace{1em}OYE32 & NADPH oxidoreductase family protein\textsuperscript{c} & ex & ex & ex & -2.90 &  &  & \\
